---
title: "Abrupt versus Gradual Motor Learning"
output:
  pdf_document: default
  html_notebook: default
---


```{r}
plot(cars)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

# Load Packages

```{r loadpackages}
library(svglite)
library(optimx)
library(ez)
```


# Load R scripts

```{r loadsources}
source('orderEffects.R') # this file deals with the order effects and runs the ANOVA
source('ExtentofLearning.R') # this file deals with the extent of learning and runs the ANOVA
source('Analysis.R') # this file has the rebound ANOVA
source('Figures.R') # this file creates the 4 figures

```


# Overview

This document discusses the figures and statistics used to investigate abrupt versus gradual motor learning. The main sections here will be looking at the Order Effects, the Extent of Learning, and the Rebound.


# Plotting All of the Behavioural Data

```{r}
plotAllData()
```


# Order Effects of Within-Subjects Design

This was done only on data from the abrupt condition, with groups (30° digitizing tablet, 60° digitalizing tablet, 30° VR setups) with the blocks (first, second, last training) as our within-subject factors, and order as our between-subject factors. The orange bars here represent the mean reach deviations of the participants who performed the abrupt condition first, and the blue bars represent the mean reach deviations of the participants who performed the gradual condition first. All of the data has been normalized to the size of the rotation.  

```{r}
plotOrderData()
```


Here is the ANOVA for each of the tablet30 group, which showed no effect of order. 
```{r}
orderANOVA(group = 'tablet30')
```

Here is the ANOVA for each of the tablet60 group, which showed no effect of order. 
```{r}
orderANOVA(group = 'tablet60')
```

Here is the ANOVA for each of the VR30 group, which showed no effect of order. 
```{r}
orderANOVA(group = 'VR30')

```


# Extent of Learning

Here we are checking if there are any differences in the extent of learning in the abrupt and gradual conditions during the last training and last reversal blocks. The data is shown for the 3 groups (30° digitizing tablet, 60° digitalizing tablet, 30° VR setups). The orange bars here represent the mean reach deviations of the abrupt condition, and the blue bars represent the mean reach deviations of gradual condition. All of the data has been normalized to the size of the rotation. 


```{r}
plotExtentofLearning()
```

Here is the ANOVA for each of the tablet30 group, which showed that there were no significant differences in the abrupt and gradual conditions. 
```{r}
ExtentOfLearningANOVA(group = 'tablet30')
```

Here is the ANOVA for each of the tablet60 group, which showed that there were no significant differences in the abrupt and gradual conditions. 
```{r}
ExtentOfLearningANOVA(group = 'tablet60')
```

Here is the ANOVA for each of the VR30 group, which showed that there were no significant differences in the abrupt and gradual conditions. 
```{r}
ExtentOfLearningANOVA(group = 'VR30')

```



# Rebound

Here we are checking if there are any differences in the rebound between the abrupt and gradual conditions for the 3 groups (30° digitizing tablet, 60° digitalizing tablet, 30° VR setups). The orange bars here represent the mean reach deviations of the abrupt condition, and the blue bars represent the mean reach deviations of gradual condition. All of the data has been normalized to the size of the rotation. 

```{r}
plotReboundData()
```

Here is the ANOVA for each of the tablet30 group, which showed that there were no significant differences in the abrupt and gradual conditions. 
```{r}
getReboundANOVA(group = 'tablet30')
```

Here is the ANOVA for each of the tablet30 group, which showed that there were no significant differences in the abrupt and gradual conditions. 
```{r}
getReboundANOVA(group = 'tablet60')
```

Here is the ANOVA for each of the tablet30 group, which showed that there were no significant differences in the abrupt and gradual conditions. 
```{r}
getReboundANOVA(group = 'VR30')
```



