---
title: "Abrupt versus Gradual Motor Learning"
output:
  pdf_document: default
  html_notebook: default
---


```{r}
plot(cars)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

# Load Packages

```{r loadpackages}
library(dplyr)
library(svglite)
library(optimx)
library(ez)
```


# Load R scripts

```{r loadsources}
source('ProcessTabletData.R')
source('Figures_tablet.R') #
source('twoRates_tablet.R')
```


# Overview

This document discusses the figures and statistics used to investigate abrupt versus gradual motor learning. The main sections here will be looking at the Rebound and the Two-Rate Model. 


# Converting angular reach deviation to a percentage of adaptation


# Order Effects of Within-Subjects Design

This was done only on data from the abrupt condition, with groups (30° digitizing tablet, 60° digitalizing tablet, 30° VR setups) and order as our between-subject factors. 

## 3 x2 ANOVA on First Block of Training
## 3 x2 ANOVA on Second Block of Training
## 3 x2 ANOVA on Final Block of Training


# Extent of Learning
# Performance on Last Block of Reversal 

We opted to split these groups into pairs for two 2 x 2 ANOVAs with first consisting of the Groups 30° and 60° digitizing tablet in order to test the effect of rotation magnitude, and the other ANOVA consisting of the Groups 30° digitizing tablet and 30° VR to test for experimental setup. This makes a total of four 2 x 2 ANOVAs for each of the dependent variables. 


# Rebound

Like for the extent of training and reversal performance, we will run two separate 2 x 2 ANOVAs for groups with the same setup but different rotations, and the two groups with the same rotation but different experimental setups across abrupt and gradual conditions.


# Two-Rate Model

## Polynomial Logistic Regression


# Plot Data

